Heatmaps of pleiotropy test statistics - all nonlocals and all locals with LOD above 15

### 2019-07-16 analysis/paper/Chr11.Rmd
updated Rmd files to get modified medations.rds files

```{r fit1_med}
nlocal <- ncol(hot_local)
nnonlocal <- ncol(hot_nonlocal)
out <- list()
medfile <- paste0("_cache/Chr", hot_chr, "_mediations.rds")
if (!file.exists(medfile)){
  for (j in 1:nlocal){
  foo <- list()
  for (i in 1:nnonlocal){
    foo[[i]] <- qtl2mediate:::fit1_med_qtl2(driver = genoprobs[[as.character(hot_chr)]][, , indices[i]],
                                             target = hot_nonlocal[ , i],
                                             mediator = hot_local[ , j],
                                             addcovar = addcovar
                                             )
  }
  out[[j]] <- foo
}
saveRDS(out, medfile)
} else {out <- readRDS(medfile)}
```

>>>>

```{r fit1_med}
nlocal <- ncol(hot_local)
nnonlocal <- ncol(hot_nonlocal)
out <- list()
medfile <- paste0("_cache/Chr", hot_chr, "_mediations.rds")
if (!file.exists(medfile)){
  for (j in 1:nlocal){
  foo <- list()
  for (i in 1:nnonlocal){
    foo[[i]] <- qtl2mediate:::fit1_med_qtl2(driver = genoprobs[[as.character(hot_chr)]][, , indices[i]],
                                             target = hot_nonlocal[ , i],
                                             mediator = hot_local[ , j],
                                             addcovar = addcovar
                                             ) %>%
        mutate(local_gene_id = colnames(hot_local)[j], 
               nonlocal_gene_id = colnames(hot_nonlocal)[i]
               )
  }
  out[[j]] <- foo
}
saveRDS(out, medfile)
} else {out <- readRDS(medfile)}
```

### 2019-07-16 analysis/paper/Chr2.Rmd
updated Rmd files to get modified medations.rds files

```{r fit1_med}
nlocal <- ncol(hot_local)
nnonlocal <- ncol(hot_nonlocal)
out <- list()
medfile <- "_cache/Chr2_mediations.rds"
if (!file.exists(medfile)){
  for (j in 1:nlocal){
  foo <- list()
  for (i in 1:nnonlocal){
    foo[[i]] <- qtl2mediate:::fit1_med_qtl2(driver = genoprobs[[as.character(hot_chr)]][, , indices[i]],
                                             target = hot_nonlocal[ , i],
                                             mediator = hot_local[ , j],
                                             addcovar = addcovar
                                             )
  }
  out[[j]] <- foo
}
saveRDS(out, medfile)
} else {out <- readRDS(medfile)}
```

@@

```{r tabulate, message=FALSE, warning = FALSE}
tib <- out %>%
  purrr::map(bind_rows) %>%
  bind_rows() %>%
  as_tibble() %>%
  rename(lod_without_med = lod_no_med, lod_with_med = lod_med) %>%
  mutate(lod_diff = lod_without_med - lod_with_med, lod_diff_proportion = lod_diff / lod_without_med) %>%
  mutate(local_gene_id = rep(colnames(hot_local), each = nnonlocal), nonlocal_gene_id = rep(colnames(hot_nonlocal), times = nlocal)) %>%
  left_join(local_annot2, by = c("local_gene_id" = "annot.id")) %>%
  left_join(nonlocal_annot, by = c("nonlocal_gene_id" = "annot.id")) %>%
  dplyr::select(symbol.x, symbol.y, lod_without_med, lod_with_med, lod_diff, lod_diff_proportion, local_gene_id, nonlocal_gene_id) %>%
  rename(local_symbol = symbol.x, nonlocal_symbol = symbol.y)
```

>>>>

```{r fit1_med}
nlocal <- ncol(hot_local)
nnonlocal <- ncol(hot_nonlocal)
out <- list()
medfile <- "_cache/Chr2_mediations.rds"
if (!file.exists(medfile)){
  for (j in 1:nlocal){
    foo <- list()
    for (i in 1:nnonlocal){
      foo[[i]] <- qtl2mediate:::fit1_med_qtl2(driver = genoprobs[[as.character(hot_chr)]][, , indices[i]],
                                             target = hot_nonlocal[ , i],
                                             mediator = hot_local[ , j],
                                             addcovar = addcovar
                                             ) %>%
        mutate(local_gene_id = colnames(hot_local)[j], 
               nonlocal_gene_id = colnames(hot_nonlocal)[i]
               )
  }
  out[[j]] <- foo
}
saveRDS(out, medfile)
} else {out <- readRDS(medfile)}
```

@@

```{r tabulate, message=FALSE, warning = FALSE}
tib <- out %>%
  purrr::map(bind_rows) %>%
  bind_rows() %>%
  as_tibble() %>%
  rename(lod_without_med = lod_no_med, lod_with_med = lod_med) %>%
  mutate(lod_diff = lod_without_med - lod_with_med, lod_diff_proportion = lod_diff / lod_without_med) %>%
  left_join(local_annot2, by = c("local_gene_id" = "annot.id")) %>%
  left_join(nonlocal_annot, by = c("nonlocal_gene_id" = "annot.id")) %>%
  dplyr::select(symbol.x, symbol.y, lod_without_med, lod_with_med, lod_diff, lod_diff_proportion, local_gene_id, nonlocal_gene_id) %>%
  rename(local_symbol = symbol.x, nonlocal_symbol = symbol.y)
```

### 2019-07-16 analysis/paper/heatmaps-pleiotropy-statistics-subset-locals.Rmd
updated Rmd files to get modified medations.rds files

```{r subset_expr_matrix-2}
hot_local <- dataset.islet.rnaseq$expr[, colnames(dataset.islet.rnaseq$expr) %in% local_annot2$annot.id]
hot_nonlocal <- dataset.islet.rnaseq$expr[, colnames(dataset.islet.rnaseq$expr) %in% nonlocal_annot$annot.id]
nnonlocal <- ncol(hot_nonlocal)
nlocal <- ncol(hot_local)
```

```{r tabulate-2, message=FALSE, warning = FALSE, eval = FALSE}
med_tib <- med_list %>%
  purrr::map(bind_rows) %>%
  bind_rows() %>%
  as_tibble() %>%
  rename(lod_without_med = lod_no_med, lod_with_med = lod_med) %>%
  mutate(lod_diff = lod_without_med - lod_with_med, lod_diff_proportion = lod_diff / lod_without_med) %>%
  mutate(local_gene_id = rep(colnames(hot_local), each = nnonlocal), nonlocal_gene_id = rep(colnames(hot_nonlocal), times = nlocal)) %>%
  left_join(local_annot2, by = c("local_gene_id" = "annot.id")) %>%
  left_join(nonlocal_annot, by = c("nonlocal_gene_id" = "annot.id")) %>%
  dplyr::select(symbol.x, symbol.y, lod_without_med, lod_with_med, lod_diff, lod_diff_proportion, local_gene_id, nonlocal_gene_id) %>%
  rename(local_symbol = symbol.x, nonlocal_symbol = symbol.y)
```

@@

```{r heat-pleio-2}
heatmaply(pm, symm = TRUE, cexRow = 0.2, cexCol = 0.2, row_side_colors = scols)
```

@@

>>>>

```{r subset_expr_matrix-2}
hot_local <- dataset.islet.rnaseq$expr[, colnames(dataset.islet.rnaseq$expr) %in% local_annot2$annot.id]
hot_nonlocal <- dataset.islet.rnaseq$expr[, colnames(dataset.islet.rnaseq$expr) %in% nonlocal_annot$annot.id]
nnonlocal <- nrow(nonlocal_annot)
nlocal <- nrow(local_annot2)
```

```{r tabulate-2, message=FALSE, warning = FALSE}
med_tib <- med_list %>%
  purrr::map(bind_rows) %>%
  bind_rows() %>%
  as_tibble() %>%
  rename(lod_without_med = lod_no_med, lod_with_med = lod_med) %>%
  mutate(lod_diff = lod_without_med - lod_with_med, lod_diff_proportion = lod_diff / lod_without_med) %>%
  left_join(local_annot2, by = c("local_gene_id" = "annot.id")) %>%
  left_join(nonlocal_annot, by = c("nonlocal_gene_id" = "annot.id")) %>%
  dplyr::select(symbol.x, symbol.y, lod_without_med, lod_with_med, lod_diff, lod_diff_proportion, local_gene_id, nonlocal_gene_id) %>%
  rename(local_symbol = symbol.x, nonlocal_symbol = symbol.y)
```

@@

```{r heat-pleio-2}
heatmaply(pm, symm = TRUE, cexRow = 0.2, cexCol = 0.2, row_side_colors = scols, limits = c(0,4))
```

@@

```{r}
pm %>%
  apply(FUN = hotspots::trunc2, MARGIN = 2, threshold = 5) %>%
  (function(x) {rownames(x) <- colnames(x); return(x)}) %>%
  heatmaply(cexRow = 0.2, cexCol = 0.2, symm = TRUE, row_side_colors = scols, limits = c(0, 5))
